Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/introduction.tex
Added comments.

Our second contribution is an analytical model for cost estimation of amortized schedules. Originally, we hoped that optimal scheduling (under our model) was tractable, as the problem
appeared simpler than the classical scheduling problem. Unfortunately, we show that optimal scheduling is NP-hard via a reduction to the Shortest Common Supersequence (SCS) problem.
Cost modeling is important as it drives not only vectorization but optimizations such as protocol mixing and scheduling as well~\cite{Ishaq:2019, Fang:2022}.

Our most important contribution is the implementation and evaluation of the compiler framework. We demonstrate expressivity of the source language by running the compiler on \ana{X} programs; these include classical MPC benchmarks such as PSI and Biometric matching, as well as kMeans, Histogram, and others. \ana{Summarize results.}

>>>>

Our second contribution is an analytical model for cost estimation of amortized schedules. Originally, we hoped that optimal scheduling (under our model, which essentially minimizes the length of the schedule) was tractable, as the problem appeared simpler than the classical scheduling problem. Unfortunately, we show that optimal scheduling is NP-hard via a reduction to the Shortest Common Supersequence (SCS) problem. Cost modeling is important as it drives not only vectorization but optimizations such as protocol mixing and scheduling as well~\cite{Ishaq:2019, Fang:2022}.

Our most important contribution is the implementation and evaluation of the compiler framework. We demonstrate expressivity of the source language by running the compiler on \ana{X} programs with interleaved if- and for-statements; these include classical MPC benchmarks such as PSI and Biometric matching, as well as kMeans, Histogram, and others. \ana{Summarize results.}
